---
title: "Penguins Size Comparison"
author: "Hanna Weyland"
date: "11/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(effsize)
library(broom)
library(ggbeeswarm)
library(car)
```


## Part 1. T-tests

Mass comparison: male and female chinstrap penguin

```{r}
chinstraps <- penguins %>% 
  filter(species == "Chinstrap")

## Histograms
ggplot(data = chinstraps, aes(x=body_mass_g)) +
  geom_histogram(bins = 10) +
  facet_wrap(~sex)

## QQ Plot 
ggplot(data = chinstraps, aes(sample=body_mass_g)) +
  geom_qq() +
  facet_wrap(~sex)

## Get descriptive stats
chinstraps %>% 
  group_by(sex) %>% 
  summarize(
    mean_mass = mean(body_mass_g),
    median_mass = median(body_mass_g),
    sd_mass = sd(body_mass_g),
    sample_size = n()
  )

```

Get vectors of body mass for female and male chinstrap penguins separately

```{r}
chinstraps_f <- chinstraps %>% 
  filter(sex == "female") %>% 
  pull(body_mass_g)

chinstraps_m <- chinstraps %>% 
  filter(sex == "male") %>% 
  pull(body_mass_g)
```

### T-tests, a couple different ways 

1. Is there a significant difference in body mass between male and female chinstrap penguins 

```{r}
chinstrap_ttest <- t.test(chinstraps_f, chinstraps_m)
chinstrap_ttest

cohen.d(chinstraps_f, chinstraps_m)
```
There is a significant difference in body mass, and a large effect size (Cohen's *d* = -1.26). The way I'm *writing this* is not reproducible. How can we use in-line referencing of outcomes so that the values would automatically update if the values did? 

Use `broom::tidy()` to get messy model outputs into tidy data frames that are easy to reference! 

```{r}
chinstrap_out <- broom::tidy(chinstrap_ttest)
chinstrap_out
```

Are male chinstrap penguins significantly larger (body mass) than female chinstrap penguins?

```{r}
t.test(chinstraps_m, chinstraps_f, alternative = "greater")
```

